---
site: distill::distill_website
params:
  gdl_id: "18LX"
---
---
title: `r params$gdl_id`
description: | 
  Technical details
---


```{r setup, message=F}
library(GeoPressureR)
library(glue)
knitr::opts_chunk$set(echo = FALSE)

load(glue("../data/interim/{params$gdl_id}.RData"))
```

## Settings used

All the results produced here are generated with (1) the raw geolocator data, (2) the labeled files of pressure and light and (3) the parameters listed below.

```{r layout="l-page"}
kable(gpr) %>% scroll_box(width = "100%")
```

## Pressure

The labeling of pressure data is illustrated with this figure. The black dots indicates the pressure datapoint not considered in the matching. Each stationary period is illustrated by a different colored line.

```{r, layout="l-page"}
plot(tag, type="pressure")
```

```{r, layout="l-page"}
plot(pressurepath, type="ts")
```

```{r, layout="l-page"}
plot(pressurepath, type="hist")
```

```{r, layout="l-page"}
plot(tag, type="map_pressure")
```

## Light

```{r, layout="l-page"}
plot(tag, type = "twilight")
```

```{r, layout="l-page"}
barW <- median(diff(tag$param$twl_calib$x)) / 2
plot(tag$param$twl_calib)
rect(xleft = tag$param$twl_calib$x - barW, ybottom = 0, xright = tag$param$twl_calib$x + barW, ytop = tag$param$twl_calib$y, col = gray(0.5))
lines(tag$param$twl_calib, col = "red")
```

The probability map resulting from light data alone can be seen below.

```{r, layout="l-page", warning=F}
plot(tag, type = "map_light")
```

## Movement Model

```{r, layout="l-page"}
plot_graph_movement(graph)
```

## Products

```{r, layout="l-page"}
plot(marginal, path = path_most_likely)
```

```{r, layout="l-page"}
plot_path(path_simulation, leaflet = FALSE)
```

## GeoPressureViz

```{r,  eval=F, layout="l-page"}
geopressureviz(id)
```

## Stationay period information

```{r}
kable(graph$stap)
```

```{r}
graph$param
```
