---
title: Twilight Label
format: html
editor: visual
---

This script walk you through the labeling of twilight and creation of the light map.

::: callout-tip
*Delete this block when you have read!*

**If you don't have light data, delete this file!**

-  These scripts should be adapted based on your project, but the same script should run for all your tags. You can always check [the original version online](https://github.com/Rafnuss/GeoPressureTemplate/blob/main/analysis/1-label.qmd).
-   Make sure you've read the [GeoPressureManual](https://raphaelnussbaumer.com/GeoPressureManual), in particular the [twilight labelling instructions](https://raphaelnussbaumer.com/GeoPressureManual/light-map.html#manual-labelling-of-twilight), before running this script
-   Nothing is saved at the end of the script and it is meant to be like that. Only twilight label file and config.yml should be edited. Use `geopressure.R` for the final run.
:::

```{r, setup}
id <- "18LX"

knitr::opts_knit$set(root.dir = normalizePath(".."))
library(GeoPressureR)
library(ggplot2)
library(glue)
```

## Create tag

Make sure you have already created the label file with the "1-label.qmd" script. 

```{r}
tag <- tag_create(
  id = config::get("id", id),
  crop_start = config::get("crop_start", id),
  crop_end = config::get("crop_end", id)
) |>
  tag_label(quiet = TRUE) |>
  tag_set_map(
    extent = config::get("extent", id),
    scale = config::get("scale", id),
    known = config::get("known", id)
  )
```

## Create Twilight

Generate the twilight automatically. Check that `twl_offset` allows for night/day being centered on the figure, otherwise edit accordingly

```{r}
tag <- twilight_create(
  tag,
  twl_offset = config::get("twl_offset", id)
)
plot(tag, type = "twilight")
```

## Annotate twilight

```{r}
twilight_label_write(tag)
```

Open `csv` on <https://trainset.raphaelnussbaumer.com/>.

Read and check the twilight annotation

```{r}
tag <- twilight_label_read(tag)
plot(tag, type = "twilight")
```

## Compute likelihood map

```{r}
tag <- geolight_map(tag)
```

`twl_calib_adjust` and `twl_llp` can generally be left to default, but add to `config.yml` if needed.

## Check

### Check calibration

```{r}
barW <- median(diff(tag$param$twl_calib$x)) / 2
plot(tag$param$twl_calib)
rect(xleft = tag$param$twl_calib$x - barW, ybottom = 0, xright = tag$param$twl_calib$x + barW, ytop = tag$param$twl_calib$y, col = gray(0.5))
lines(tag$param$twl_calib, col = "red")
```

### Check light map

```{r}
plot(tag, type = "map_light")
```

### Check with pressure and trajectory

```{r}
geopressureviz(tag)
```
