---
title: Tag label (Advanced)
editor: source
---

This script is meant to be used by familiar users of GeoPressureTemplate. For new users, please use `1-label.qmd`. The script actually covers both `1-label.qmd` and `2-twilight.qmd`.

```{r setup}
knitr::opts_knit$set(root.dir = here::here())
library(GeoPressureR)
library(ggplot2)
library(plotly)

id <- "18LX"
```

## Sensor data and crop date

```{r crop_date}
ggplotly(
  tag_create(id, quiet = TRUE) |>
    plot(type = "pressure", plot_plotly = FALSE) +
    geom_vline(
      xintercept = c(
        as.POSIXct(config::get("tag_create", id)$crop_start),
        as.POSIXct(config::get("tag_create", id)$crop_end)
      ),
      color = "red",
      lwd = 1
    )
)
```

## Create the tag

```{r}
tag <- tag_create(
  id,
  crop_start = config::get("tag_create", id)$crop_start,
  crop_end = config::get("tag_create", id)$crop_end
)
```

## Label the tag

```{r label_trainset}
trainset(tag)
```

## Compute pressure map

```{r geopressuretemplate_tag}
geopressuretemplate_tag(
  id = id,
  tag_set_map = list(scale = 1, include_min_duration = 6),
  geopressuretemplate = list(likelihood = "map_pressure"),
  quiet = TRUE
)
```

## Geopressureviz

Directly plot the likelihood map and draw the path. Query the pressure only for the stap that need to be checked.

```{r}
geopressureviz(
  id,
  # path = tag2path(tag, interp = 1) # interpolate positions of stap lasting < 1 day.
  # path = path_geopressureviz # if already run geopressureviz
  # path = pressurepath # Use this once computed (see below)
)
```

## Twilight

Load the interim file

```{r}
load_interim(id)
```

Adjust `twl_offset`.

```{r}
tag <- twilight_create(
  tag,
  twl_offset = config::get("twilight_create", id)$twl_offset
)
plot(tag, type = "twilight")
```

Label with geolightviz

```{r}
geolightviz(tag)
```

Check labelled twilights together with the expected twilight lines from the path drawn on geopressureviz

```{r twilight_read}
tag <- twilight_label_read(tag)
plot(
  tag,
  type = "twilight",
  twilight_line = path2twilight(tag2path(tag, interp = 2)),
  plot_plotly = T
)
```

Compute light map

```{r light_map}
tag <- geolight_map(
  tag,
  twl_calib_adjust = config::get("geolight_map", id)$twl_calib_adjust,
  twl_llp = config::get("geolight_map", id)$twl_llp,
  fitted_location_duration = config::get(
    "geolight_map",
    id
  )$fitted_location_duration
)
```

```{r}
plot_twl_calib(tag)
plot_twl_calib(tag, path = tag2path(tag, interp = 2))
```

## GeoPressureViz

Refine the path and label based on pressure and light combined.

```{r}
geopressureviz(tag)
```

## Compute pressurepath

Final check with the time-consuming `pressurepath`, usually performed in `4-geopressuretemplate.R` with full resolution interim file.

```{r}
# geopressuretemplate_pressurepath(id)
load_interim(id)
plot_pressurepath(pressurepath)
plot_pressurepath(pressurepath, type = "histogram")
plot_pressurepath(pressurepath, type = "altitude")
```
