---
title: Download wind
editor: source
description: https://raphaelnussbaumer.com/GeoPressureManual/geopressuretemplate-wind.html
---

This script will help you download the wind data for a `tag` and define the movement model.

::: callout-tip
*Delete this block when you have read!*

-   These scripts should be adapted based on your project, but the same script should run for all your tags. You can always check [the original version online](https://github.com/Rafnuss/GeoPressureTemplate/blob/main/analysis/1-label.qmd).
-   Make sure you've read the [GeoPressureManual](https://raphaelnussbaumer.com/GeoPressureManual), in particular the [instructions on wind data](https://raphaelnussbaumer.com/GeoPressureManual/trajectory-with-wind.html#download-wind-data), before running this script
-   Nothing is saved at the end of the script and it is meant to be like that. Only wind file and config.yml should be edited. Use `geopressure.R` for the final run.
:::

```{r setup}
id <- "18LX"

knitr::opts_knit$set(root.dir = here::here())
library(GeoPressureR)
library(job)
```

## Set Copernicus credentials

::: callout-tip
*Delete this block when you have read!* 

If you don't yet have one, create a ECMWF account at <https://www.ecmwf.int/> and retrieve your personal access token.

Once created, you can retrieve your Personal Access Token on <https://cds.climate.copernicus.eu/profile> and save them in your environment file (i.e., `.Renviron`). You can open this file with `usethis::edit_r_environ()` and add:

```bash
cds_token =  "{Personal Access Token}"
```
:::

## Create tag

Make sure you have already created the label file with the "1-label.qmd" script.

```{r, cache = TRUE, message=FALSE}
tag <- geopressuretemplate_tag(id, quiet=F)
```

## Download wind data

The [job package](https://lindeloev.github.io/job) allows to download the wind data in the background and let your R console free to use.

```{r, eval = FALSE}
job({
  tag_download_wind(tag)
})
```

Check requests at <https://cds.climate.copernicus.eu/requests>

## Define movement model

### Add wind data

```{r}
graph <- graph_create(
  tag,
  thr_likelihood = config::get("graph_create", id)$thr_likelihood,
  thr_gs = config::get("graph_create", id)$thr_gs
)
```

```{r}
graph <- graph_add_wind(
  graph,
  pressure = tag$pressure,
  thr_as = config::get("graph_add_wind", id)$thr_as
)
```

### Set movement model

Check that the movement model defined in `config.yml` is adequate.

```{r}
graph <- graph_set_movement(graph,
  bird = bird_create(config::get("bird_create", id)$species_name)
)
```

Check the movement model

```{r}
plot_graph_movement(graph)
```

