---
title: Add wind
format: html
editor: visual
---

This script will help you download the wind data for a `tag` and define the movement model

```{r, setup}
# Choose the id
id <- "18LX"

# Set the directory to the project root
knitr::opts_knit$set(root.dir = "..")
library(GeoPressureR)
library(glue)
library(job)
```

## Load tag

Start from an existing `tag`

```{r}
load(glue("./data/interim/{id}.RData"))
```

## Set-up copernicus credential

If you don't have one, create account at <https://cds.climate.copernicus.eu/user/15631/edit> and retrieve your API key and UID number

```{r, eval = F}
Sys.setenv(cds_key = "Insert_your_CDS_API_KEY_here")
Sys.setenv(cds_user = "Insert_your_CDS_UID_here")
```

## Download wind data

```{r, eval=F}
job({
  tag_download_wind(tag)
})
```

Check requests at <https://cds.climate.copernicus.eu/cdsapp#!/yourrequests>

## Define movement model

### Add wind data

If you haven't computed a graph yet

```{r, eval = F}
graph <- graph_create(
  tag,
  thr_likelihood = config::get("thr_likelihood", id),
  thr_gs = config::get("thr_gs", id)
)
```

```{r}
graph <- graph_add_wind(
  graph,
  pressure = tag$pressure,
  thr_as = config::get("thr_as", id)
)
```

### Set movement model

Check that the movement model defined in `config.yml` is adequate.

```{r}
graph <- graph_set_movement(graph,
  bird = bird_create(config::get("scientific_name", id)),
  power2prob = config::get("movement_low_speed_fix", id),
  low_speed_fix = config::get("movement_low_speed_fix", id)
)
plot_graph_movement(graph)
```
